\chapter{Introduction}
\label{cha:intro}

This thesis work was developed during a 4 month internship at U-Hopper, with which I was able to combine a work experience in a company with the writing of the bachelor's thesis. U-Hopper is a research-intensive deep-tech SME, headquartered in Trento, providing big data-enabled solutions and technologies for the government, retail and manufacturing sectors. U-Hopper has received numerous awards for its innovative solutions, including, among the others, the Lamarck prize (2013), a EC Seal of Excellence (2015), the Innov@Retail prize (2016) and a nomination for the 2017 EC Innovation Radar Awards. Life event detection can be a significant business for the company, because it is already into the user profiling world, with a product called Tapoi\footnote{\url{www.tapoi.me}}, but above all because detect a life event into someone's life can bring many opportunity with banks, insurances, estate agents and many other businesses, which are constantly looking for such a meaningful information like a life event can be.

According to Cambridge Dictionary\footnote{\url{dictionary.cambridge.org}}, a \emph{life event} is \textit{"a very important event in someone's life, such as marriage, the birth of a child, or the death of a family member"}. These kind of events are quite rare in a lifetime, and they may bring with them a big charge of stress, and big changes for those who live them. Furthermore, they do not last only for the day they happen, but there is a medium or long period that is influenced by the event: for example, a pregnancy lasts for 40 weeks, or a wedding is usually organized in several months; but also a negative life event, like the death of someone dear, causes bad feelings for a period more or less long for those who live it. The Holmes and Rahe stress scale \cite{holmes1967social} puts in relation several life events for the load of stress they cause: on a scale from 0 to 100, the most stressful event for an adult is the death of a spouse, that scores 100, but also positive events are part of this list, such as marriage, with the score of 50, and a pregnancy, with 40. In addition, a life event can be followed by another one life event: for example in Italy, 80\% of births occur within a marriage in 2012\footnote{\url{www.istat.it/it/files//2015/02/Avere_Figli.pdf}}.

Therefore, a life event is a signal of many factors in who lives it. If it is detected in time, it can be a great opportunity for many entities, such as banks, insurance companies and other kinds of ad-hoc marketing campaigns. The life events have a deep effect on the individual's spending habits and purchase patterns. For example, according to the results\footnote{\url{travelbehaviour.files.wordpress.com/2014/06/lttb_carownbriefingnote_16-june.pdf}} of a study made by the University of the West of England about the relationship between life events and travel behaviour \cite{chatterjee2015facts}, households are more likely to change the number of cars at the time of life events: the "\textit{Birth of a child increases likelihood of a non-car owning household acquiring a car and increases likelihood of a two-car owning household relinquishing a car. This suggests households seek a one car solution when having children}".

The identification of a life event into social media contents is a \emph{machine learning} problem, and to be more precise, a classification one. Machine learning is a field of computer science which deals with allowing a computer system to "\textit{learn with data, without being explicitly programmed}" \cite{samuel1959some}. It can be applied in many contexts, such as taking decisions, or make optimizations, forecasts and predictions. Nowadays a human being faces itself with machine learning in everyday life: home assistants, security surveillance, music and shopping suggestions, customer services are strongly powered by artificial intelligence. These services relies on data to learn how to work as good as possible: they are trained with samples of data similar to what they expect to receive by their users: the more accurate, exhaustive and in large quantities they are, the better the system learns. Therefore, data have a very central role in machine learning problems.

A classification task has the goal of assigning a belonging class to a given object. The input is composed by a tuple of \emph{features} that characterize the object, usually made by numbers, and the output is a categorical variable, such as a "yes/no" label. In other words, it can be seen as a mathematical function, that maps a vector $ \boldsymbol{x} \in \mathbb{R}^n $ to an answer $ y \in C $
\begin{gather*}
\begin{split}
f & \colon \mathbb{R}^n \to C \\
f & \colon \boldsymbol{x} \mapsto y
\end{split}
\end{gather*}
where $C$ is a set of possible categories. A famous educational example of this kind of problem is the Iris flower classification\footnote{\url{en.wikipedia.org/wiki/Iris_flower_data_set}}, where the input $ \boldsymbol{x} $ is composed by the sepal and petal widths and lengths in cm of the flower, and $C = \{\text{\texttt{Iris setosa}, \texttt{Iris virginica}, \texttt{Iris versicolor}}\}$. For each sample composed by 4 measures the belonging class is predicted.

The background of live event identification on social media consists in a huge stream of documents, called \emph{posts}, each one written by a specific user and containing text, images, external links and other attachments, with a date of publication. Every user can share, comment or like someone else's post. A \emph{timeline} is the list of posts written by a single user, sorted by decreasing date of publication. These data are accessible through the Web (in some cases the author's authorization is necessary to get them) and contain many information. There is an endless number of works that use social media data for various purposes, and in this case they are used to detect events.

\section{Research objectives}
Life event detection on social media is still an open problem; in fact, such a commercial solution to be integrated into a social system of some commercial, banking or insurance entity does not exist, not even an accademic pubblication that goes beyond a classification problem. Therefore, the reseach question is the following: \emph{is it feasible to detect the occurrence of life events based on social media user activities?}

The goal of this thesis is to find a way to understand whether a person has lived a life event, or if she is about to live it, observing her activities on social media. Nowadays, social media are widely used all over the world: according to the Global Digital 2018 report\footnote{\url{wearesocial.com/it/blog/2018/01/global-digital-report-2018}}, 3.196 billions of people use social media every month, sharing messages, photos and other contents that are also about their private life. They are used to deliver messages of congratulations or support, to search for information from users who have experienced certain situations or to make announcements of news or changes. Consequently, social media are one of the best platform to get reliable information about people in an easy, fast and free way.

The idea is to design a hybrid system that combines a data driven approach to analyze each post, and a model driven solution to inspect a user's timeline, in order to find out whether the user has lived a life event according to what she shared on social media. This work is focused on the detection of two life events, marriages and births of a child.

\section{Detection vs prediction}

A user's timeline is composed by all the posts published from the time she signed up to the social media up to today. From this data is possible to \emph{detect} an event that happened in the past. Event detection is the identification of an event that occurred, into a stream of data, and now it is finished or at most it is still ongoing. Another possibility is to \emph{predict} an event, understanding whether the event can occur in a more or less near future. Event prediction can be done in several ways, for example observing what happen in the user's past, or in timelines of users with similar age, location and preferences, or using some logical model: for example, a married person will likely have a baby in her lifetime.

Of course, the two things have a very different meaning. With event detection is possible to understand what a person lived in the past, what she might searched or needed at the time of the event, and which are her usual needs: for example, if it is known that a user had a child, her possible future vehicle will be a family car, or her new house should probably have at least two bedrooms. With event prediction is possible to anticipate some user's choices or needs, giving her some ad-hoc offers and advertising campaign: for example, if it was known that a user would probably have a child in the near future, she would likely look for a new bedroom furniture or a new bigger car.

From the machine learning point of view there is no big differences between event detection and event prediction. In both cases the usual patterns that indicate that the event is about to occur are the same. The only difference is that the detection is based on facts, and so it is possible to say whether the obtained result is correct or not, while prediction is based on suppositions, which are not always verifiable. This thesis is focused on life event detection, so on what the user has lived.

\section{Outline}

This thesis work is organized as follows: in Chapter 2 the state of the art is introduced, explaining what is missing for this purpose and what has to be changed. In addition, the data situation about life event will be shown, unfolding a solution that is different from the standard text classification. In Chapter 3 the design solution is presented, with a particular focus on the logical behind the system and on the used algorithms. Chapter 4 is about the implementation procedure and the performance evaluation of a prototype of the system, and finally, in Chapter 5 some final remarks and observations for future developments are presented.

